---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scene

<!-- badges: start -->
<!-- badges: end -->

The goal of scene is to ...

## Installation

You can install the development version of scene like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

Get imagery, this uses recent dates and a small extent around a longlat (see `scene()`). 

By default we get the "best" images from all available. Internally we sort by "solar day" (scenes taken at the same time, but possibly spread over tiles and/or zones). Atm "best" is defined by information content (super rough, just we look at the least compressible scenes). 


'date' is treated like a date range (if you get a stac error go further back in time for the max.) You can input strings like "2024" or "2024-02" for intervals, or a full range of date-times. 

```{r example}
options(parallelly.fork.enable = TRUE, future.rng.onMisuse = "ignore")
library(furrr); plan(multicore)
x <- scene:::scene(date = Sys.Date() + c(-180, -2), keep = 4L)
plan(sequential)


library(terra)
par(mfrow = n2mfrow(nrow(x)))
jk <- lapply(x$dsn, \(.x) plotRGB(rast(.x)))
x$date

```


Other approaches use a "median" approach, this is just part of ongoing experimentation for small areas. 


